### 2017-10-13 Gruba/02-overview.tex

\stitle{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator for visualization.
%For the time being, Profile Demonstrator presents \tbc{}.

The distinctive feature of System  \sys{} is to model user \retg{} behaviors over groups instead of the mono model for all users.

>>>>

\stitle{Demonstrator.} At the top layer of \sys{}, it is the Demonstrator for visualizing all aspects of the system, e.g., profiling of user groups.
%For the time being, Profile Demonstrator presents \tbc{}.

As shown above, the distinctive feature of System  \sys{} is to model user \retg{} behaviors over groups instead of the mono model for all users.
